Computer Science House Constitution

### 2023-10-09 constitution.tex
Removed Section formerly 5.D.2.A.4.C, Alternate Housing, which violates RIT housing (#20)
* Removed Section formerly 5.D.2.A.4.C

* Re-added Three Tiered Vote

---------

Co-authored-by: Sam-Cordry <samcordry@gmail.com>
Co-authored-by: Robert Hochgraf <robehoco@gmail.com>
Resolve #7 Fix Financial Information/Calculations in 5.D.1.C (#34)
* Draft New Language for 5.D.1.C

* Update Draft per Feedback

\asection{Operations}
\asubsection{Operations of the Financial Directorship}
\asubsubsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\asubsubsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
Additional time and reduction of dues may both be given to a member in an appropriate situation.
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
After this date, dues collection is suspended until the start of the next academic year.
\asubsubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{|l c|}
\hline
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Public Relations & 5\% \\
\hline
Accumulated & 5\% \\
\hline
\end{tabular}
\end{center}

The suggested total operational budget is \$8064.
This figure is based on yearly estimated on-floor member dues (\$160 x 72 members = \$11520) minus the 10\% reserved for Accumulated (Accum).
Money allocated for Accum and off-floor member dues is deposited into the CSH Account and saved.

@@

\asection{Number of Votes Required}
The Number of Votes Required refers to the numbers required to achieve a quorum and for a vote to pass.
Below are listed four standard votes.
Numbers for non-standard votes are defined in the section describing the actual vote.
\asubsection{Simple Majority}
In a Simple Majority Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
\asubsection{Fifty Percent}
In a Fifty Percent Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
\asubsection{Two-Thirds}
In a Two-thirds Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
\asubsection{Three-Quarters}
In a Three-Quarters Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds three-quarters the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.

\asubsection{Alternative}
The winning option is selected outright if it gains more than half the votes cast as a first preference.
If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
This process continues until one option has half of the votes cast and is elected.

>>>>

\asection{Operations}
\asubsection{Operations of the Financial Directorship}
\asubsubsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\asubsubsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
Additional time and reduction of dues may both be given to a member in an appropriate situation.
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
After this date, dues collection is suspended until the start of the next academic year.
\asubsubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{|l c|}
\hline
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Public Relations & 5\% \\
\hline
Accumulated & 5\% \\
\hline
\end{tabular}
\end{center}

% The suggested total operating budget is $8360.
% This figure comes from having approximately 55 on-floor members with $80 per semester dues (totaling $8800) minus 5% set aside for Accumulated.

Dues collected from on-floor members are to be distributed into directorship budgets as shown in the above table.
Money allocated for Accumulated or collected from off-floor members is deposited into the CSH Account and saved.

@@

\asection{Number of Votes Required}
The Number of Votes Required refers to the numbers required to achieve a quorum and for a vote to pass.
Below are listed four standard votes.
Numbers for non-standard votes are defined in the section describing the actual vote.
\asubsection{Simple Majority}
In a Simple Majority Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
\asubsection{Fifty Percent}
In a Fifty Percent Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
\asubsection{Two-Thirds}
In a Two-thirds Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
\asubsection{Three-Quarters}
In a Three-Quarters Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds three-quarters the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.
\asubsection{Alternative}
The winning option is selected outright if it gains more than half the votes cast as a first preference.
If not, the option with the fewest number of first preference votes is eliminated and their votes move to the second preference marked on the ballot papers.
This process continues until one option has half of the votes cast and is elected.
